Multidimensional signals and analytic flexibility: Estimating degrees of freedom in human speech analyses

### 2022-09-24 RR_manuscript/Draft_RR.tex
clean up code, remove unused objects, simplify table labels, make sure table values match prose

Eighty-four teams initially signed up to participate in the study.
Fifty-four of the signed-up teams dropped out during the analysis phase.
One Team Coordinator, Wim van Dommelen (who agreed to their feedback being shared), gave the following reason: ``{[}T{]}he project's approach is too much top-down instead of bottom-up. {[}\ldots{]} I would rather prefer to explore the collected utterances and run different types of acoustic analyses, which would then be followed by statistical evaluation of the data.''
We find that this contribution clearly speaks to the main objective of the current study: investigate researcher's degrees of freedom in the speech sciences.
Based on our personal experience with research in the field, it is common practice to test as many different types of models, using as many different types of measurements, to answer one research question.

Thirty teams submitted their analysis by the established deadline.
These are the teams that are included in this study.
Submitting teams consisted of an average of 3.6 individual analysts (SD = 2.8).
Upon sign-up, we collected background information from each analyst through the intake form, which was administered during Phase 1, prior to the data being released to the teams.
Analysts had on average 4.8 years (SD = 4.2) of experience after completing their PhD, ranging from -3.8 years, i.e.~PhD students (or younger) to 12.4 years.
The analysts' prior belief in the effect under investigation, on a scale from 0 to 100, ranged from 48.5 to 92.0 with an average of 69.2 (SD = 11.3).
We take this to suggest that analysts had an overall rather high positive prior belief in the investigated relationship between prosody and word combination typicality.

At the end of Phase 2 (primary data analysis), the teams have submitted a grand total 104 individual models to answer the research question, with a mean of 3.7 (SD: 3.4) models per team.
Table \ref{tab:descriptives-table} provides a summary of the contributing teams and their analyses.
Crucially, the analytic approaches employed by the teams varied widely both in the acoustical analyses of the speech signal and in the statistical analyses of the obtained measures.
We proceed to discuss these in the following sections, after which we provide an overview of the peer-review ratings.

\vspace{0.2in}

@@

\vspace{0.2in}

@@

Based on statistical framework, type of model, distribution family, fixed terms, and not including random effects, there were a total of 47 different model specifications.
When considering both acoustic and statistical analysis, we have found a grand total of 104, i.e.~each submitted analysis was unique.
Of the 104 submitted models, 37 include a statistically reliable effect (21.76\%).
Nine teams out of the thirty (30\%) reported to have found at least one statistically reliable effect.

@@

\caption{\label{tab:descriptives-table}Descriptive statistics of contributing teams (n = 30), acoustic 
    analyses, and statistical analyses.}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{llrr}
\toprule
\bf{Team characteristics} &    & \bf{Range} & \bf{Mean (SD)}\\
\midrule
 & Team size & 1.0 -- 12.0 & 3.6 (2.8)\\
 & Years after phd & -3.8 -- 12.4 & 4.8 (4.2)\\
 & Self-report statistical ability & 33.0 -- 93.3 & 69.5 (16.5)\\
 & Prior belief & 48.5 -- 92.0 & 69.2 (11.3)\\
 & Acoustic analysis rating & 41.2 -- 88.3 & 71.5 (13.9)\\
 & Peer rating & 39.0 -- 88.7 & 70.0 (14.3)\\
 &  &  \vphantom{5} & \\
\bf{Acoustic analyses} &  & \bf{n} & \bf{\%}\\
\midrule
\hspace{1em}Outcome & F0 & 37 & 35.6\\
 & Duration & 36 & 34.6\\
 & Intensity & 15 & 14.4\\
 & Formants & 13 & 12.5\\
 & Other & 3 & 2.9\\
 &  &  \vphantom{4} & \\
\hspace{1em}Temporal window & Segment & 47 & 45.6\\
 & Word & 45 & 43.7\\
 & Sentence & 4 & 3.9\\
 & Phrase & 3 & 2.9\\
 & Other & 4 & 3.9\\
 &  &  \vphantom{3} & \\
\hspace{1em}Typicality operationalization & Categorical & 75 & 72.8\\
 & Continuous (mean) & 25 & 24.3\\
 & Continuous (median) & 3 & 2.9\\
 &  &  \vphantom{2} & \\
\bf{Statistical analyses} &  & \bf{n} & \bf{\%}\\
\midrule
\hspace{1em}Framework & Frequentist & 86 & 82.7\\
 & Bayesian & 18 & 17.3\\
 &  &  \vphantom{1} & \\
\hspace{1em}Model & Linear model & 102 & 98.1\\
 & Gam & 1 & 1.0\\
 & Other & 1 & 1.0\\
 &  &  & \\
 &  & \bf{Range} & \bf{Mean (SD)}\\
\hspace{1em}N & Models & 1 -- 16 & 3.7 (3.4)\\
 & Coefficients & 1 -- 11 & 3.5 (2.7)\\
 & Predictors & 1 -- 4 & 1.6 (0.9)\\
 & Random effects & 0 -- 10 & 2.5 (2.1)\\
 & Random intercepts & 0 -- 10 & 1.9 (1.8)\\
 & Random slopes & 0 -- 4 & 0.6 (1.1)\\
 & Terms & 1 -- 4 & 1.8 (1.1)\\
\bottomrule
\end{tabular}}
\end{table}

@@

Teams reviewed each others' acoustic and statistical analyses.
The mean rating of the acoustic analyses, on a scale from 0 to 100, is 74.5 (SD = 11.2, see Table \ref{tab:descriptives-table}).
The mean rating of the statistical analysis is 73.8 (SD = 14.1).
For reference, as mentioned in the Methods section, a score of 75 was defined as ``an imperfect analysis but the needed changes are unlikely to dramatically alter the final interpretation'', indicating that on average reviewers judged the provided analyses to be appropriate, although ``imperfect''.

@@

\ref{fig:plot-meta1} illustrates the individual intercepts for critical typicality coefficients across models and teams, sorted in ascending order based on their mean.
Given the nature and wide variety of acoustic operationalizations, there is not always a natural interpretation of the scale, but in most cases a positive effect corresponds to typical word combinations eliciting higher acoustic values (e.g.~longer duration, higher f0, etc.), as mentioned above.
When looking at the raw estimates and their variance (grey triangles and lines), it is striking how much teams' estimates differed.
Estimates ranged between -0.6544004 to 0.9885856 standard units.

@@

For example, for those analyses that investigated the duration of segments (e.g.~the duration of the second vowel in \emph{Banana}), the reported duration measures exhibit standard deviations that range from 33.4 to 51.4 ms.
These standard deviations allow us to convert the meta analytical estimates into milliseconds by multiplying those values with the standard units.
The reported effect estimates from teams varied between -0.6544004 and 0.9885856 standard units which corresponds to duration values ranging from -21.856972 to 50.8132988.
A more conservative approach is to convert the meta-analytic estimates of between-model variation, thus obtaining an estimate of between-model variability in milliseconds that ranges between 7.4 and 15.1 at 95\% credibility.\footnote{The calculation is thus: the minimum standard deviation of duration multiplied by the lower limit of the 95\% CrI of the between-models variability estimate, times 1.96 to obtain a 95\% CrI: \(33.4 * 0.11 = 3.8\), \(3.8 * 1.96 = 7.4\) ms; the maximum standard deviation of duration multiplied by the upper limit of the 95\% CrI of the between-models variability estimate, time 1.96: \(51.4 * 0.15 = 7.7\), \(7.7 * 1.96 = 15.1\) ms}.

While this might not immediately strike one as a lot of variation, it crosses several theoretically relevant thresholds for perception and articulation:
For example, previous studies reported statistically robust effects of 8 and 16 ms \citep{coretta2019}, down to 4.5 ms \citep{nowak2006}.
Another example is the phenomenon of incomplete neutralization, a widely studies phenomenon, which involves duration effects ranging 7-15 ms \citep{nicenboim2018using}.
This particular phenomenon has sparked long-lasting methodological and theoretical debates about the very nature of linguistic representations \citep{port2005against}.

Expecting random variation between different analysts of 7 to 15 in one or the other direction is thus concerning and might lead to opposing theoretical conclusions.

@@

Second and independent of a possible true relationship, certain measurement choices might be associated with stronger expectations relative to the research question, which might lead to stronger researcher biases.
Many analysts that participated in this study targeted measures related to fundamental frequency (f0), since similar functional relationships like information structure and predictability can be expressed by f0 \citep[e.g.][]{grice2017integrating, turnbull2017role}.
Moreover, prior work has actually suggested a relationship between typicality and f0 \citep[e.g.][]{dimitrova2008prosodic, dimitrova2009did}.
Participating analysts might have been aware of those findings, which might have, subconsciously of otherwise, nudged their choices into one particular direction.

Regardless of its cause, we have to conclude that depending on the choice of how the speech signal is operationalized, researchers might find evidence for or against a theoretically relevant effect.
This conclusion is further supported by the fact that between-team variability was lower than between model variability.
This is an important observation when put into context of the fact that most teams submitted many different models.

Teams submitted up to 16 different models to test for a possible relationship between typicality and the speech signal.
The complexity of the speech signal lends itself to multiple approaches, but this plurality of hypothesis tests invites bias and can dramatically increase the rate of falsely claiming the presence of an effect \citep{roettger2019researcher}.
When operating within the frequentist inferential framework, testing the same hypothesis with different dependent variables is known to increase the false-positive (Type-I error) rate, if not corrected for \citep{tukey1953}.
Another possible outcome of analytic flexibility as seen in this study is selective reporting of those tests that yield a desirable outcome \citep[\citet{john2012measuring}, \citet{simmons2011false}]{kerr1998harking}, while null results remain unreported \citep[e.g.,][\citet{rosenthal1979file}]{sterling1959publication}.
Fields such as the speech sciences that make theoretical advances based on multidimensional data should be aware of this flexibility and calibrate their confidence in empirical claims accordingly.

@@

The current results point to important barriers for successful accumulation of knowledge.
The replication crisis has brought attention to scientific practices that lead to unreliable and biased claims in the literature \citep[e.g.,][\citet{fidler2018reproducibility}]{vazire2017quality}.
One of the suggested paths forward is for researchers to directly replicate previous studies more often \citep[e.g.,][]{open2015estimating, camerer2018evaluating}.
While we agree with the importance of direct replications, our study (and similar crowd-sourced analyses before us) suggest that replicating more is simply not enough.
There is only limited value in learning that a particular procedure is replicable if the idiosyncratic nature of the procedure itself might not yield a representative result relative to all possible procedures that could have been applied to the research question.
Beyond a replication crisis, quantitative disciplines are going through what has been called an ``inference crisis'' \citep{rotello2015more, starns2019assessing}.
As shown by the peer-ratings of the analyses reported in this study, well-trained and experienced speech researchers not only applied completely different approaches to the same research question, but also considered most of these alternative approaches acceptable.
Being aware of this idiosyncratic variation between analysts should lead to more nuanced claims and what Breznau et al.~refers to as ``epistemic humility''.

@@

We should ideally specify the link between conceptual construct and quantitative system---the ``derivation chain'' \citep{dubin1970theory, meehl1990summaries}---prior to data collection and analysis, including defining constructs and their relationship within the quantitative system, specifying auxiliary assumptions and boundary conditions, and defining target measurements, statistical expectations and possible (and impossible) effect magnitudes.
Without well defined derivation chains, we ``are not even wrong'' \citep{scheel2022most} because falsified expectations cannot tell us much about the conceptual constructs they are based on when the relationship between the two is underspecified.

In light of the observed analytic flexibility, what can we do to appropriately calibrate our confidence in our claims?
First of all, through sharing of materials, data and statistical protocols, we can make our idiosyncratic choices transparent to others \citep{munafo2017manifesto, vazire2017quality}.
It further enables the evaluation and verification of underlying claims and allows for the evaluation of empirical, computational and statistical reproducibility \citep{lebel2018unified}.
It allows for alternative analyses to establish analytic robustness \citep{steegen2016increasing} and strengthens attempts to synthesize evidence via meta-analyses \citep[e.g.,][]{nicenboim2018using}
Given that minor procedural changes can sometimes drastically affect the final interpretation of the results \citep{breznau2021observing}, we should ideally share a detailed documentation of the data collection procedure, the measurement choices, the data extraction, and statistical analyses.
Within fields that deal with speech data, open source software that allows to extract acoustic parameters via reproducible scripts can help other researchers to trace back seemingly inconsequential choices during the measurement process \citep[e.g., Praat:][EMU: \citet{winkelmann2017emu}, the Montreal Forced Aligner \citet{mcauliffe2017},]{boersma2021praat}.

Second, making analytic pathways completely re-traceable does not change the fact that analysts apply different analytic approaches.
Crowd-sourced projects such as the current one can shed light on the range of degrees of freedom during analysis and help producing a consensual estimated effect using meta-analytic techniques.
This is obviously not always feasible in terms of required resources and time, but could be a consideration for claims that have large epistemological or practical consequences.

@@

In light of these possible sources of bias, a field can benefit from explicit positionality statements \citep[e.g.,][\citet{darwin2020}, \citet{fox2021open}]{jafar2018}.
Researchers do not analyse data in a vacuum.
It is important recognize and disclose one's positionality, i.e., a reflection about how educational background, social identity, power, experience and context might influence researchers approaches and interpretations.

Despite of all these possible sources of bias and uncertainty, our study suggests that at least the minimum variability that we can expect to find is the variability that we have observed.

Finally, our study focussed on the speech sciences.
The generalizability of our findings to other disciplines on the one hand and specifically other sub-disciplines of the language sciences is, of course, limited.
We focused on quantitative analyses that require operationalization of a multidimensional signal.
While some of our results can be informative for other disciplines that work with speech or video signals, they might not be very informative for expected variation between analysts working in qualitative research fields.
This is an important point to make because the cognitive sciences in general, and the language sciences in particular have many research areas that are investigated using qualitative methods rather than quantitatively.
It is conceivable that the discussed issues apply differently or not at all to qualitative data analyses.

>>>>

Eighty-four teams initially signed up to participate in the study, comprising 211 analysts.
Fifty-four of the signed-up teams dropped out during the analysis phase.

Thirty teams submitted their analysis by the established deadline.
These are the teams that are included in this study.
The submitting teams comprised 109 analysts, with an average of 3.6 (SD = 2.8) individuals per team.
Upon sign-up, we collected background information from each analyst through the intake form, which was administered during Phase 1, prior to the data being released to the teams.
Analysts had on average 4.8 years (SD = 4.2) of experience after completing their PhD, ranging from -3.8 years, i.e.~PhD students (or younger) to 12.4 years, suggesting that, on average, analyst were experienced researchers.
The analysts' prior belief in the effect under investigation, on a scale from 0 to 100, ranged from 48.5 to 92.0 with an average of 69.2 (SD = 11.3).
We take this to suggest that analysts had an overall rather high positive prior belief in the investigated relationship between acoustics and word combination typicality.

At the end of Phase 2 (primary data analysis), the teams have submitted a grand total 104 individual models to answer the research question, with a mean of 3.6 (SD: 3.4) models per team.
Table \ref{tab:descriptives-table} provides a summary of the contributing teams and their analyses.
Crucially, the analytic approaches employed by the teams varied widely both in the acoustical analyses of the speech signal and in the statistical analyses of the obtained measures.
We proceed to discuss these in the following sections, after which we provide an overview of the peer-review ratings.

@@

@@

Based on statistical framework, type of model, distribution family, fixed terms, and not including random effects, there were a total of 47 different model specifications.

When considering both acoustic and statistical analysis, we have found a grand total of 104 different analytic pipelines.
In other words, each individual submitted analysis was unique.
Of the 104 submitted models, 37 were reported to show a statistically reliable effect (21.8\%).
Nine teams out of the thirty (30\%) reported to have found at least one statistically reliable effect.

@@

\caption{\label{tab:descriptives-table}Descriptive statistics of teams, acoustic analyses, and statistical analyses included in the meta-analysis. The data set included analyses from 30 teams and  109 analysts.}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{llrr}
\toprule
\bf{Team characteristics} &    & \bf{Range} & \bf{Mean (SD)}\\
\midrule
 & Team size & 1.0 -- 12.0 & 3.6 (2.8)\\
 & Years after phd & -3.8 -- 12.4 & 4.8 (4.2)\\
 & Prior belief & 48.5 -- 92.0 & 69.2 (11.3)\\
 & Acoustic analysis peer rating & 41.2 -- 88.3 & 71.5 (13.9)\\
 & Statistical analysis peer rating & 33.0 -- 93.3 & 69.5 (16.5)\\
 & Overall peer rating & 39.0 -- 88.7 & 70.0 (14.3)\\
 &  &  \vphantom{5} & \\
\bf{Acoustic analyses} &  & \bf{n} & \bf{\%}\\
\midrule
\hspace{1em}Outcome & F0 & 37 & 35.6\\
 & Duration & 36 & 34.6\\
 & Intensity & 15 & 14.4\\
 & Formants & 13 & 12.5\\
 & Other & 3 & 2.9\\
 &  &  \vphantom{4} & \\
\hspace{1em}Temporal window & Segment & 47 & 45.6\\
 & Word & 45 & 43.7\\
 & Sentence & 4 & 3.9\\
 & Phrase & 3 & 2.9\\
 & Other & 4 & 3.9\\
 &  &  \vphantom{3} & \\
\hspace{1em}Typicality operationalization & Categorical & 75 & 72.8\\
 & Continuous (mean) & 25 & 24.3\\
 & Continuous (median) & 3 & 2.9\\
 &  &  \vphantom{2} & \\
\bf{Statistical analyses} &  & \bf{n} & \bf{\%}\\
\midrule
\hspace{1em}Framework & Frequentist & 86 & 82.7\\
 & Bayesian & 18 & 17.3\\
 &  &  \vphantom{1} & \\
\hspace{1em}Model & Linear model & 102 & 98.1\\
 & Gam & 1 & 1.0\\
 & Other & 1 & 1.0\\
 &  &  & \\
 &  & \bf{Range} & \bf{Mean (SD)}\\
\hspace{1em}N & Models & 1 -- 16 & 3.6 (3.4)\\
 & Predictors & 1 -- 5 & 2.0 (1.2)\\
 & Random terms & 1 -- 10 & 2.5 (1.3)\\
\hspace{1em} & \hspace{1em}Intercept & \hspace{1em}1 -- 10 & \hspace{1em}1.9 (1.0)\\
\hspace{1em} & \hspace{1em}Slope & \hspace{1em}0 -- 4 & \hspace{1em}0.5 (0.9)\\
\bottomrule
\end{tabular}}
\end{table}

@@

Teams reviewed each others' acoustic and statistical analyses.
The mean rating of the acoustic analyses, on a scale from 0 to 100, is 71.5 (SD = 13.9, see Table \ref{tab:descriptives-table}).
The mean rating of the statistical analysis is 69.5 (SD = 16.5).
For reference, as mentioned in the Methods section, a score of 75 was defined as ``an imperfect analysis but the needed changes are unlikely to dramatically alter the final interpretation'', indicating that on average reviewers judged the provided analyses to be appropriate, although ``imperfect''.

@@

Figure \ref{fig:plot-meta1} illustrates the individual intercepts for critical typicality coefficients across models and teams, sorted in ascending order based on their mean.
Given the nature and wide variety of acoustic operationalizations, there is not always a natural interpretation of the scale, but in most cases a positive effect corresponds to typical word combinations eliciting higher acoustic values (e.g.~longer duration, higher f0, etc.), as mentioned above.
When looking at the raw estimates and their variance (grey triangles and lines), it is striking how much teams' estimates differed.
Estimates ranged between -0.65 to 0.99 standard units.

@@

For example, for those analyses that investigated the duration of segments (e.g.~the duration of the second vowel in \emph{Banana}), the reported duration measures exhibit standard deviations that range from 33.4 to 51.4 ms.
These standard deviations allow us to convert the meta analytical estimates into milliseconds by multiplying those values with the standard units.
The reported effect estimates from teams varied between -0.65 and 0.99 standard units which corresponds to duration values ranging from -21.86 to 50.81.
A more conservative approach is to convert the meta-analytic estimates of between-model variation, thus obtaining an estimate of between-model variability in milliseconds that ranges between 7.4 and 15.1 at 95\% credibility.\footnote{The calculation is thus: the minimum standard deviation of duration multiplied by the lower limit of the 95\% CrI of the between-models variability estimate, times 1.96 to obtain a 95\% CrI: \(33.4 * 0.11 = 3.8\), \(3.8 * 1.96 = 7.4\) ms; the maximum standard deviation of duration multiplied by the upper limit of the 95\% CrI of the between-models variability estimate, time 1.96: \(51.4 * 0.15 = 7.7\), \(7.7 * 1.96 = 15.1\) ms}.

While this might not immediately strike one as a lot of variation, it crosses several theoretically relevant thresholds for perception and articulation:
For example, the phenomenon of incomplete neutralization, a widely studied phenomenon, involves duration effects ranging from 7 to 15 ms \citep{nicenboim2018using}. This particular phenomenon has sparked long-lasting methodological and theoretical debates about the very nature of linguistic representations \citep{port2005against}.
Vowel duration differences within this range have been reported across phenomena, associated with segmental contrasts \citep{coretta2019}, reduction \citep{nowak2006}, and biomechanical reflexes of prominence \citep{mucke2014effect}.
Expecting random variation between different analysts of 7 to 15 in one or the other direction can be theoretically relevant and might lead to opposing theoretical conclusions.

@@

Second and orthogonal to a possible true relationship, certain measurement choices might be associated with stronger expectations relative to the research question, which might lead to stronger researcher biases.
Many analysts targeted measures related to fundamental frequency (f0), likely because similar functional relationships like information structure and predictability can be expressed by f0 \citep[e.g.][]{grice2017integrating, turnbull2017role}.
Moreover, prior work has actually suggested a relationship between typicality and f0 \citep[e.g.][]{dimitrova2008prosodic, dimitrova2009did}.
Participating analysts might have been aware of those findings, which might have, subconsciously or otherwise, nudged their choices into one particular direction.

Regardless of its cause, we have to conclude that depending on the choice of how the speech signal is operationalized, researchers might find evidence for or against a theoretically relevant effect.
This conclusion is further supported by the fact that between-team variability was lower than between model variability.
This is an important observation when put into context of the fact that most teams submitted many different models.
Teams submitted up to 16 different models to test for a possible relationship between typicality and the speech signal.
The complexity of the speech signal lends itself to multiple approaches, but this plurality of hypothesis tests invites bias and can dramatically increase the rate of falsely claiming the presence of an effect \citep[\citet{simmons2011false}]{roettger2019researcher}.
One team coordinator gave the following reason for dropping out of the project (and allowed us to share this statement): ``{[}T{]}he project's approach is too much top-down instead of bottom-up. {[}\ldots{]} I would rather prefer to explore the collected utterances and run different types of acoustic analyses, which would then be followed by statistical evaluation of the data.''
We find that this statement speaks to the main objective of the current study: investigate researcher's degrees of freedom in the speech sciences.
Based on our personal experience with research in the field, it is common practice to test as many different types of models, using as many different types of measurements, to answer one research question.
When operating within the frequentist inferential framework, testing the same hypothesis with different dependent variables is known to increase the false-positive (Type-I error) rate, if not corrected for \citep{tukey1953}.
Another possible outcome of analytic flexibility as seen in this study is selective reporting of those tests that yield a desirable outcome \citep[\citet{john2012measuring}, \citet{simmons2011false}]{kerr1998harking}, while null results remain unreported \citep[\citet{rosenthal1979file}]{sterling1959publication}.
Fields such as the speech sciences that make theoretical advances based on multidimensional data should be aware of this flexibility and calibrate their confidence in empirical claims accordingly.

@@

The current results point to important barriers for successful accumulation of knowledge.
The replication crisis has brought attention to scientific practices that lead to unreliable and biased claims in the literature \citep[\citet{fidler2018reproducibility}]{vazire2017quality}.
One of the suggested paths forward is for researchers to directly replicate previous studies more often \citep[\citet{camerer2018evaluating}]{open2015estimating}.
While we agree with the importance of direct replications, our study (and similar crowd-sourced analyses before us) suggest that replicating more is simply not enough.
There is only limited value in learning that a particular procedure is replicable if the idiosyncratic nature of the procedure itself might not yield a representative result relative to all possible procedures that could have been applied to the research question.
Beyond a replication crisis, quantitative disciplines are going through what has been called an ``inference crisis'' \citep[\citet{starns2019assessing}]{rotello2015more}.
As shown by the peer-ratings of the analyses reported in this study, well-trained and experienced speech researchers not only applied completely different approaches to the same research question, but also considered most of these alternative approaches acceptable.
Being aware of this idiosyncratic variation between analysts should lead to more nuanced claims and what Breznau et al.~refers to as ``epistemic humility''.

@@

We should ideally specify the link between conceptual construct and quantitative system---the ``derivation chain'' \citep[\citet{meehl1990summaries}]{dubin1970theory}---prior to data collection and analysis, including defining constructs and their relationship within the quantitative system, specifying auxiliary assumptions and boundary conditions, and defining target measurements, statistical expectations and possible (and impossible) effect magnitudes.
Without well defined derivation chains, we ``are not even wrong'' \citep{scheel2022most} because falsified expectations cannot tell us much about the conceptual constructs they are based on when the relationship between the two is underspecified.

In light of the observed analytic flexibility, what can we do to appropriately calibrate our confidence in our claims?
First of all, through sharing of materials, data and statistical protocols, we can make our idiosyncratic choices transparent to others \citep{munafo2017manifesto, vazire2017quality}.
It further enables the evaluation and verification of underlying claims and allows for the evaluation of empirical, computational and statistical reproducibility \citep{lebel2018unified}.
It allows for alternative analyses to establish analytic robustness \citep{steegen2016increasing} and strengthens attempts to synthesize evidence via meta-analyses \citep[e.g.,][]{nicenboim2018using}
Given that minor procedural changes can sometimes drastically affect the final interpretation of the results \citep{breznau2021observing}, we should ideally share a detailed documentation of the data collection procedure, the measurement choices, the data extraction, and statistical analyses.
Within fields that deal with speech data, open source software that allows to extract acoustic parameters via reproducible scripts can help other researchers to trace back seemingly inconsequential choices during the measurement process \citetext{\citealp[e.g., Praat:][]{boersma2021praat}; \citealp[EMU:][]{winkelmann2017emu}; \citealp[the Montreal Forced Aligner:][]{mcauliffe2017}}.

Second, making analytic pathways completely re-traceable does not change the fact that analysts apply idiosyncratic analytic approaches.
Crowd-sourced projects such as the current one can shed light on the range of degrees of freedom during analysis and help producing a consensual estimated effect using meta-analytic techniques.
This is obviously not always feasible in terms of required resources and time, but could be a consideration for claims that have large epistemological or practical consequences.

@@

In light of these possible sources of bias, a field can benefit from explicit positionality statements \citep[e.g.,][]{jafar2018, darwin2020, fox2021open}.
Researchers do not analyse data in a vacuum.
It is important recognize and disclose one's positionality, i.e., a reflection about how educational background, social identity, power, experience and context might influence researchers' approaches and interpretations.

Despite of all these possible sources of bias and uncertainty, our study suggests that at least the minimum variability that we can expect to find across researchers is the rather concerning variability that we have observed.

Finally, our study focused on the speech sciences.
The generalizability of our findings to other disciplines on the one hand and specifically other sub-disciplines of the language sciences is, of course, limited.
We focused on quantitative analyses that require operationalization of a multidimensional signal.
While some of our results can be informative for other disciplines that work with speech or video signals, they might not be very informative for expected variation between analysts working in qualitative research fields.
This is an important point to make because the cognitive sciences in general, and the language sciences in particular have many research areas that are based on qualitative methods.
It is conceivable that the discussed issues apply differently or not at all to qualitative data analyses.
